Common sense approaches to sharing tabular data alongside publication

### 2021-08-13 response-letter/response-letter.Rmd

our_table <- read_sheet(ss = our_table_id,
                        .name_repair = janitor::make_clean_names) %>% 
  select(ID = id, 
         comment = reviewer_comment, 
         response) %>% 
  mutate(comment = 
           case_when(
             ID == "R1-2" ~ new_comment_line,
             TRUE ~ comment
           )) 
```

Dear Dr. Callaghan,

Thank you for considering our commentary article “Incentives are the biggest barriers to widespread data sharing” for publication in Patterns.

We thank the reviewers for time and detailed comments. We have addressed comments from the reviewers and believe the paper is clearer and better as a result. Our response to individual reviewer comments are presented in the table on page 2 of this letter.

### 2021-08-17 response-letter/response-letter.Rmd

```{r read-sheet, include = FALSE}
our_table_id <- gs4_get(
  "1fIl8jy72XWD4liFZVlx6WvsnXp7ld8fs7eZvwVJpSy0"
  )

our_table <- read_sheet(ss = our_table_id,
                        .name_repair = janitor::make_clean_names) %>% 
  select(ID = id, 
         comment = reviewer_comment, 
         response) %>% 
  mutate(comment = 
           case_when(
             ID == "R1-2" ~ new_comment_line,
             TRUE ~ comment
           )) 
```

Dear Dr. Callaghan,

Thank you for considering our commentary article, "Common sense approaches to sharing tabular data alongside publication" (previously titled "Incentives are the biggest barriers to widespread data sharing"), for publication in Patterns.

### 2021-09-14 new-paper.Rmd
change paper title
address comment R1-2

---
title: Incentives are the biggest barriers to widespread data sharing
author: Nicholas J. Tierney\* (1, 2, 3) & Karthik Ram\* (4)
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
citation_package: 'natbib'
csl: nature-communications.csl
header-includes:
  - \setstretch{1.45}
  - \usepackage[utf8]{inputenc}
---

@@

Journals provide data papers in a formal publication explaining data that is archived. This is a familiar avenue for researchers to receive credit and citation. Writing a data paper can be very useful for researchers, but, data papers lack guidelines on how to structure data for effective reuse and sharing. Partner with Dryad to link archived data with research papers. Dryad will also provide professionals to curate your data, thereby improving usability.

>>>>

---
title: "Common sense approaches to sharing tabular data alongside publication"
author: Nicholas J. Tierney\* (1, 2, 3) & Karthik Ram\* (4)
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
citation_package: 'natbib'
csl: nature-communications.csl
header-includes:
  - \setstretch{1.45}
  - \usepackage[utf8]{inputenc}
---

@@

Journals provide data papers in a formal publication explaining data that is archived. This is a familiar avenue for researchers to receive credit and citation. Writing a data paper can be very useful for researchers, but, data papers lack guidelines on how to structure data for effective reuse and sharing. Partner with Dryad to link archived data with research papers. Dryad will also provide professionals to curate your data, thereby improving usability. While writing a data paper can be very useful for researchers, journals that publish data papers lack guidelines on how to structure data for effective reuse and sharing.
